Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-16 paper/sheaf_lics.tex

At total, with other files containing technical lemmas, the project
contains 6322 lines.

\nt{describe how many line for each, be clear about what has not been formalized}

>>>>

At total, with other files containing technical lemmas, the project
contains 6322 lines.
%\nt{describe how many line for each, be clear about what has not been formalized}

In our formalization, some things are admitted, either because they
are just an adaptation of a proposition already formalized
in~\cite{hottbook}, either because they are true, but very technical~:
\begin{itemize}
\item in \texttt{modalities.v}, an equality is admitted in the proof
  of proposition~\ref{sec:defin-basic-prop}.
\item in \texttt{nat\_lemmas.v}, the proof that $\IsHProp (n\leqslant
  m)$ is admitted.
\item in \texttt{sheaf\_induction.v}, in the proof that
  $C(\mu_T)=(C\id)$ (see lemma~\ref{lem:sepiscolim}), we admit the proof
  of equality of projections.
\item in \texttt{sheaf\_induction.v}, we admit some very technical
  proofs in proofs that $\square$ and $\star$ are modalities.
\item in \texttt{sheaf\_induction.v}, cumulativity is an axiom,
  because of universes issues.
\end{itemize}

Some other lemmas are proved, then admitted. We do it so that Coq
doesn't constrain too much universes, without having to explicitly
annotate universes everywhere in the formalization.

The main issue in this formalization is the gestion of universes in
Coq~\cite{sozeau2014universe}. If Coq can handle cumulativity on all
$\Type$, it is not the case for the sigma type $\Type_n$. This issue
can be solved by adding an axiom of cumulativity for $\Type_n$, but as
it would not have any computational content, it would really
complicates the proofs.

Moreover, even the definition of successive sheafification types is
not allowed~:

\[ \left\{
    \begin{array}{l}
      \modal_{-1} = \lambda T:\HProp,~ \lnot\lnot T \\
      \displaystyle{\modal_{n+1} = \lambda T:\Type_{n+1}},\\
      \quad \displaystyle{\sum_{u:T \to \Type_n^\modal} \modal_{-1} 
      \left\|
      \sum_{a:T} u = (\lambda t,~\modal_n (a=t))
      \right\|}
    \end{array}
  \right.,\]
because Coq asks for every $\modal_n$ to have the same universes
levels. Thus, the induction presented in this paper cannot be
formalized at the moment. We only present the induction step.
